Music Classification Using Convolutional Neural Networks

### 2019-12-15 docs/paper.tex
add abstract

    \begin{abstract}
        The abstract paragraph should be indented \nicefrac{1}{2}~inch (3~picas) on
        both the left- and right-hand margins. Use 10~point type, with a vertical
        spacing (leading) of 11~points. The word \textbf{Abstract} must be centered,
        bold, and in point size 12. Two line spaces precede the abstract. The abstract
        must be limited to one paragraph.
    \end{abstract}

>>>>

\begin{abstract}
	In this paper we describe a convolutional neural network designed to classify music by genre.
	The base idea came from an article we read about the combination of CNN and mathematical algorithms for a music classification \cite{sample}.
	At the moment the network can categorise at a 61\% accuracy.
	We use the GTZAN dataset with slight modifications as it covers all our needs.
	During the building of this network we encountered numerous challenges, especially with the activation functions.
	A constant problem was overlearning, which we could only delay. 
\end{abstract}
